Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/background.tex
more text squeezing

In this paper, we denote a map $m$ as a set of pairs of keys and values, in which each key appears at most once.
For any map $m$,  $m(k)$ is the value paired with the key $k$ in $m$. We denote by $m[x\to y]$ a map that maps $x$ to $y$, and every other key $k$ to $m(k)$.

@@

The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
\textit{interprocedural} \textit{distributive} \textit{environment}
problems. An \textit{environment} problem is one whose data-flow
lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the data-flow functions to be distributive.

@@

The meet of two environment transformers $t_1, t_2$ can be computed by taking the union of the edges
in their pointwise representations. When the same edge appears in the pointwise representations of
both $t_1$ and $t_2$, the micro-function for that edge in $t_1 \sqcap t_2$ is the meet of the
micro-functions for that same edge in $t_1$ and in $t_2$.

@@

The IDE algorithm operates on the same exploded supergraph as the IFDS algorithm
(except that the edges are labelled with micro-functions). For each pair $(n,d)$ of
node and fact, the algorithm computes a micro-function equal to the meet of the micro-functions
of all the realizable paths from the program entry point to the pair.

>>>>

We denote a map $m$ as a set of pairs of keys and values, with each key appearing at most once.
For a map $m$,  $m(k)$ is the value paired with the key $k$. We denote by $m[x\to y]$ a map that maps $x$ to $y$ and every other key $k$ to $m(k)$.

@@

The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
\textit{interprocedural} \textit{distributive} \textit{environment}
problems. An IDE problem is one whose data-flow
lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the data-flow functions to be distributive.

@@

The meet of two environment transformers $t_1, t_2$ is computed as the union of the edges
in their pointwise representations. When the same edge appears in the pointwise representations of
both $t_1$ and $t_2$, the micro-function for that edge in $t_1 \sqcap t_2$ is the meet of the
micro-functions for that same edge in $t_1$ and in $t_2$.

@@

The IDE algorithm operates on the same exploded supergraph as the IFDS algorithm
(but its edges are labelled with micro-functions). For each pair $(n,d)$ of
node and fact, IDE computes a micro-function equal to the meet of the micro-functions
of all the realizable paths from the program entry point to the pair.

### 2015-03-17 sas2015/content/impl.tex
text squeezing
more text squeezing

Conceptually, micro-functions are functions from $L$ to $L$, where $L$
is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. 
The IDE algorithm requires an efficient representation of micro-functions.
The chosen representation needs to support the basic micro-functions that
we presented in Section~\ref{seq:transIfdsIde}, and it must
support function application, comparison, and be closed under function composition
and meet. We now propose such a representation for the correlated-calls micro-functions.

@@

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
so this running time must be multiplied by the cost of evaluating a
micro-function. We show that the micro-functions in the correlated-calls
IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
is $O(ED^3\rcc T)$. Note that in practice, $\rcc$ is much smaller
than $R$, so Lemma~\ref{lem:onlycorrrec} is significant for 
performance.

>>>>

Conceptually, micro-functions are functions from $L$ to $L$, where $L$
is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. 
The IDE algorithm requires an efficient representation of micro-functions.
The representation must support the basic micro-functions that
we presented in Section~\ref{seq:transIfdsIde}, and it must
support function application, comparison, and be closed under function composition
and meet. We now propose such a representation for the correlated-calls micro-functions.

@@

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
so this running time must be multiplied by the cost of evaluating a
micro-function. We show that the micro-functions in the correlated-calls
IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
is $O(ED^3\rcc T)$. In practice, $\rcc$ is much smaller
than $R$, so Lemma~\ref{lem:onlycorrrec} is significant for 
performance.
